Environmental pathogen reservoirs and habitat heterogeneity in a metapopulation

### 2014-07-23 Manuscript/manuscript.tex
Updates to figures
small changes to figures, and updating figure captions.

\begin{figure}
\centering
\includegraphics[height=7cm]{highlow(full).pdf}
\caption{The effect of the presence of high and low quality patches on (a) mean susceptible occupancy, (b) mean infectious occupancy, and (c) mean total occupancy, measured relative to  a low variance metapopulation.  Red solid lines show hiqh quality metapopulations, blue dashed show low quality, and black shows high variance.}
\label{sens}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=7cm]{infevents(full).pdf}
\caption{The number of infection events ($S$ to $I$ transitions) for individual patches in endemic simulations.  Light gray lines show smoothed fit for single simulations, while the thick black line shows the smoothed fit over all simulations.  The thin black lines show the smoothed fits for longevities of 40 (top) and 140 (bottom).}
\label{infections}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[height=5.5cm]{metapop(lattice).pdf}
\caption{Percent of simulations resulting in (a) endemic disease (both susceptibles and infectiouss persist) and (b) pandemic disease (no susceptibles persist), as a function of the pathogen's environmental longevity (half-life of infectivity decay) and the variance of the patch quality distribution.}
\label{poutcome_lattice}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{highlow(lattice).pdf}
\caption{The effect of the presence of high and low quality patches on (a) mean susceptible occupancy, (b) mean infectious occupancy, and (c) mean total occupancy, measured relative to  a low variance metapopulation.  Red solid lines show hiqh quality metapopulations, blue dashed show low quality, and black shows high variance.}
\label{sens_lattice}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{infevents(lattice).pdf}
\caption{The number of infection events ($S$ to $I$ transitions) for individual patches in endemic simulations.  Light gray lines show smoothed fit for single simulations, while the thick black line shows the smoothed fit over all simulations.  The thin black lines show the smoothed fits for longevities of 40 (bottom) and 140 (top).}
\label{infections_lattice}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[height=5.5cm]{metapop(x0).pdf}
\caption{Percent of simulations resulting in (a) endemic disease (both susceptibles and infectiouss persist) and (b) pandemic disease (no susceptibles persist), as a function of the pathogen's environmental longevity (half-life of infectivity decay) and the variance of the patch quality distribution.}
\label{poutcome_x0}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{highlow(x0).pdf}
\caption{The effect of the presence of high and low quality patches on (a) mean susceptible occupancy, (b) mean infectious occupancy, and (c) mean total occupancy, measured relative to  a low variance metapopulation.  Red solid lines show hiqh quality metapopulations, blue dashed show low quality, and black shows high variance.}
\label{sens_x0}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{infevents(x0).pdf}
\caption{The number of infection events ($S$ to $I$ transitions) for individual patches in endemic simulations.  Light gray lines show smoothed fit for single simulations, while the thick black line shows the smoothed fit over all simulations.  The thin black lines show the smoothed fits for longevities of 40 (top) and 140 (bottom).}
\label{infections_x0}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[height=5.5cm]{metapop(delta).pdf}
\caption{Percent of simulations resulting in (a) endemic disease (both susceptibles and infectiouss persist) and (b) pandemic disease (no susceptibles persist), as a function of the pathogen's environmental longevity (half-life of infectivity decay) and the variance of the patch quality distribution.}
\label{poutcome_delta}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{highlow(delta).pdf}
\caption{The effect of the presence of high and low quality patches on (a) mean susceptible occupancy, (b) mean infectious occupancy, and (c) mean total occupancy, measured relative to  a low variance metapopulation.  Red solid lines show hiqh quality metapopulations, blue dashed show low quality, and black shows high variance.}
\label{sens_delta}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{infevents(delta).pdf}
\caption{The number of infection events ($S$ to $I$ transitions) for individual patches in endemic simulations.  Light gray lines show smoothed fit for single simulations, while the thick black line shows the smoothed fit over all simulations.  The thin black lines show the smoothed fits for longevities of 60 (bottom) and 120 (top).}
\label{infections_delta}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[height=7cm]{highlow(full).pdf}
\caption{The effect of the presence of high and low quality patches on (a) mean susceptible occupancy, (b) mean infectious occupancy, and (c) mean total occupancy.  Red solid lines show hiqh quality metapopulations, blue dashed show low quality, black shows high variance, and gray shows low variance.}
\label{sens}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=7cm]{infevents(full).pdf}
\caption{The number of infection events ($S$ to $I$ transitions) for individual patches in endemic simulations.  Light gray lines show smoothed fit for single simulations, while the thick black line shows the smoothed trend over all simulations.}
\label{infections}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[height=5.5cm]{metapop(lattice).pdf}
\caption{Mean occupancy of (a) susceptible patches, (b) infectious patches, and (c) both, as a function of the pathogen's environmental longevity (half-life of infectivity decay) and the variance of the patch quality distribution.}
\label{poutcome_lattice}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{highlow(lattice).pdf}
\caption{The effect of the presence of high and low quality patches on (a) mean susceptible occupancy, (b) mean infectious occupancy, and (c) mean total occupancy.  Red solid lines show hiqh quality metapopulations, blue dashed show low quality, black shows high variance, and gray shows low variance.}
\label{sens_lattice}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{infevents(lattice).pdf}
\caption{The number of infection events ($S$ to $I$ transitions) for individual patches in endemic simulations.  Light gray lines show smoothed fit for single simulations, while the thick black line shows the smoothed trend over all simulations.}
\label{infections_lattice}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[height=5.5cm]{metapop(alpha0).pdf}
\caption{Mean occupancy of (a) susceptible patches, (b) infectious patches, and (c) both, as a function of the pathogen's environmental longevity (half-life of infectivity decay) and the variance of the patch quality distribution.}
\label{poutcome_x0}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{highlow(alpha0).pdf}
\caption{The effect of the presence of high and low quality patches on (a) mean susceptible occupancy, (b) mean infectious occupancy, and (c) mean total occupancy.  Red solid lines show hiqh quality metapopulations, blue dashed show low quality, black shows high variance, and gray shows low variance.}
\label{sens_x0}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{infevents(alpha0).pdf}
\caption{The number of infection events ($S$ to $I$ transitions) for individual patches in endemic simulations.  Light gray lines show smoothed fit for single simulations, while the thick black line shows the smoothed trend over all simulations.}
\label{infections_x0}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[height=5.5cm]{metapop(delta).pdf}
\caption{Mean occupancy of (a) susceptible patches, (b) infectious patches, and (c) both, as a function of the pathogen's environmental longevity (half-life of infectivity decay) and the variance of the patch quality distribution.}
\label{poutcome_delta}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{highlow(delta).pdf}
\caption{The effect of the presence of high and low quality patches on (a) mean susceptible occupancy, (b) mean infectious occupancy, and (c) mean total occupancy.  Red solid lines show hiqh quality metapopulations, blue dashed show low quality, black shows high variance, and gray shows low variance.}
\label{sens_delta}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=7cm]{infevents(delta).pdf}
\caption{The number of infection events ($S$ to $I$ transitions) for individual patches in endemic simulations.  Light gray lines show smoothed fit for single simulations, while the thick black line shows the smoothed trend over all simulations.}
\label{infections_delta}
\end{figure}
